MSDS6372Project1

### 2021-02-01 MSDS6372Project1.Rmd
testing

par(mfrow=c(2,2))
plot(log.model7)
library(olsrr)
ols_plot_cooksd_bar(log.model1)
ols_plot_resid_stand(log.model1)
# Residual looks okay~
# Now try MSRP without log transformation

>>>>

par(mfrow=c(2,2))
plot(log.model7)
library(olsrr)
ols_plot_cooksd_bar(log.model7)
ols_plot_resid_stand(log.model7)
# Residual looks okay~
# Now try MSRP without log transformation
